Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure

### 2017-06-10 documents/TriangleScenarioArXiv/ts.tex
Changed all of the inequalities to a canonical form where violation is a maximization above zero

    The first causal compatibility inequality is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \cdots \\
    \cdots + P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
    \end{gathered}
    \end{equation*}
    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure (i.e. factorizes according to \cref{eq:compatibility_as_factorization}) must satisfy \cref{eq:ww_ineq}. As a demonstration, the Fritz distribution violates \cref{eq:ww_ineq}. Notice the final term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $-1$. For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$. Consequently we conclude that the Fritz distribution is incompatible with the Triangle structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.

@@

    It is possible to simplify \cref{eq:ww_ineq} identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$. Upon doing so, one obtains the following,
    \begin{gather*}
        P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + \cdots \\
        \cdots + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0) - P_{ABC}(000)P_{C}(3) - P_{ABC}(021)P_{C}(2) + \cdots \\
        \cdots - P_{ABC}(202) - P_{ABC}(302) - P_{ABC}(233)P_{C}(0) - P_{AC}(33)P_{C}(0) \geq 0
    \end{gather*}

>>>>

    The first causal compatibility inequality is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure (i.e. factorizes according to \cref{eq:compatibility_as_factorization}) must satisfy \cref{eq:ww_ineq}. As a demonstration, the Fritz distribution violates \cref{eq:ww_ineq}. Notice the first term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $+1$. For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $0.0129\ldots \not \leq 0$. Consequently we conclude that the Fritz distribution is incompatible with the Triangle structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.

@@

    It is possible to simplify \cref{eq:ww_ineq} by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$. Upon doing so, one obtains the following,
    \begin{gather*}
        + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
        - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
        - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
    \end{gather*}
